Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-09-30 grove-paper.tex
Rework figures (Michael D. Adams)

%% Packages
\usepackage{booktabs}
\usepackage[rule=false]{subcaption}
\usepackage{graphicx}
\usepackage{semantic}
\let\colonapprox\undefined % Avoid redefinition error in `colonequals`
\let\colonsim\undefined % Avoid redefinition error in `colonequals`
\usepackage{colonequals}
\usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{fontawesome}

@@

\tikzset{
  every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{graphs/graph style/.style={
  tree layout,
  level sep=1cm,
  nodes={draw, rounded corners=1mm},
  edges={draw, font={\small\ttfamily}},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{0}$}
}}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
TODO
\caption{User interface}
\label{fig:A simple tree with a hole-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "root", > "1"'] -> {
   "$\texttt{var(x)}_{4}$" [> "left", > "3"'],
   {}
  }
 }
};
\end{tikzpicture}
\caption{Graph representation}
\label{fig:A simple tree with a hole-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole}
\label{fig:A simple tree with a hole}
\end{figure}

@@

\begin{figure}
\begin{tabular}{|p{0.49\linewidth}|p{0.49\linewidth}|}
%\centering
TODO
&
%\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Rt$_1$"] -> {
   "$\texttt{x}_{4}$" [> "L$_3$"'],
   "$\texttt{y}_{6}$" [> "R$_5$"]
  }
 }
};
\end{tikzpicture}
\\
\subcaption{User interface}
\label{fig:Construction-a}
 &
\subcaption{\autoref{fig:A simple tree with a hole-b} after adding \Vertex{6} and \Edge{5}}
\label{fig:Construction-b}
\\ \hline
\end{tabular}
\caption{Construction}
\label{fig:Construction}
\end{figure}

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
TODO
\caption{User interface}
\label{fig:Construction-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Rt$_1$"] -> {
   "$\texttt{x}_{4}$" [> "L$_3$"'],
   "$\texttt{y}_{6}$" [> "R$_5$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:A simple tree with a hole-b} after adding \Vertex{6} and \Edge{5}}
\label{fig:Construction-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction}
\label{fig:Construction}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "root", > "1"'] -> {
   "$\texttt{x}_{4}$" [> "left", > "3"'],
   {}
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 y [as={$\texttt{y}_{6}$}]
};
\end{tikzpicture}
\caption{\autoref{fig:Construction-b} after deleting \Edge{5}}
\label{fig:Change-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}[framed]
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "RT$_1$"] -> {
   "$\texttt{x}_{4}$" [> "L$_3$"'],
   "$\texttt{z}_{8}$" [> "R$_7$"]
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 "$\texttt{y}_{6}$"
};
\end{tikzpicture}
\caption{\autoref{fig:Change-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Change-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Change}
\label{fig:Change}
\end{figure}

@@

\begin{figure*}
% TODO: naive add that creates a conflict
% \begin{tikzpicture}
% \path (0,0)       node {\includegraphics[scale=0.4]{graphviz/wrapping/1.dot}};
% \path (0cm,-4cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/2.dot}};
% \path (0cm,-8cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/3.dot}};
% \path (0cm,-12cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/4.dot}};
% \path (0cm,-16cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/5.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (-1cm,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{var(x)}_{4}$" [> "left", > "3"'],
  "$\texttt{var(z)}_{6}$" [> "right", > "5"']
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Change-b} after deleting \Edge{1}}
\label{fig:Wrapping-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"']
 }
};
\path (-1cm,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{var(x)}_{4}$" [> "left", > "3"'],
  "$\texttt{var(z)}_{6}$" [> "right", > "5"']
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Wrapping-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "9"'] -> {
    "$\texttt{var(x)}_{4}$" [> "left", > "3"'],
    "$\texttt{var(z)}_{6}$" [> "right", > "5"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-b} after adding \Edge{9}}
\label{fig:Wrapping-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure*}

@@

\begin{figure}
% \centering
% \begin{tikzpicture}
% \path (0,0)    node {\includegraphics[scale=0.75]{graphviz/move/1.dot}};
% \path (0,-5cm) node {\includegraphics[scale=0.75]{graphviz/move/2.dot}};
% \path (0,-9cm) node {\includegraphics[scale=0.75]{graphviz/move/3.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"']
 }
};
\path (0cm,-3cm) graph [graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{var(x)}_{4}$" [> "left", > "3"'],
  "$\texttt{var(z)}_{6}$" [> "right", > "5"']
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-c} after deleting \Edge{9}}
\label{fig:Move-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   {},
   "$\texttt{*}_{2}$" [> "right", > "11"'] -> {
    "$\texttt{var(x)}_{4}$" [> "left", > "3"'],
    "$\texttt{var(z)}_{6}$" [> "right", > "5"']
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-a} after adding \Edge{11}}
\label{fig:Move-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \Vertex{2} from the left child to the right child of \Vertex{8}}
\label{fig:Move}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   {},
   "$\texttt{*}_{2}$" [> "right", > "11"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(z)}_{6}$" [> "right", > "5"']
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   {},
   "$\texttt{*}_{2}$" [> "right", > "11"'] -> {
    "$\texttt{var(x)}_{4}$" [> "left", > "3"'],
    "$\texttt{var(v)}_{14}$" [> "right", > "15"']
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   {},
   "$\texttt{*}_{2}$" [> "right", > "11"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(v)}_{14}$" [> "right", > "15"']
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   {},
   "$\texttt{*}_{2}$" [> "right", > "11"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Different Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(v)}_{14}$" [> "right", > "15"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Different Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   {
    "$\texttt{var(x)}_{20}$" [> "right", > "21"']
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   "$\texttt{var(y)}_{22}$" [> "right", > "23"']
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   {
    "$\texttt{var(x)}_{20}$" [> "right", > "21"'],
    "$\texttt{var(y)}_{22}$" [> "right", > "23"']
   }
  }
 }
};
\end{tikzpicture}

TODO: show UI
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] -> {
    "$\texttt{var(x)}_{26}$" [> "left", > "25"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}

>>>>

%% Packages
\usepackage{booktabs}
\usepackage[rule=false]{subcaption}
\usepackage{graphicx}
\usepackage{semantic}
\let\colonapprox\undefined % Avoid redefinition error in `colonequals`
\let\colonsim\undefined % Avoid redefinition error in `colonequals`
\usepackage{colonequals}
\usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{fontawesome}
\usepackage{array}

@@

\tikzset{
  every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{edge style/.style={
  draw,
  font={\small\ttfamily},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/graph style/.style={
  tree layout,
  level sep=1cm,
  nodes={draw, rounded corners=1mm},
  edges={edge style},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{0}$}
}}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
TODO
\caption{User interface}
\label{fig:A simple tree with a hole-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"],
   {}
  }
 }
};
\end{tikzpicture}
\caption{Graph representation}
\label{fig:A simple tree with a hole-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole}
\label{fig:A simple tree with a hole}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
TODO
\caption{User interface}
\label{fig:Construction-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"'],
   "$\texttt{y}_{6}$" [> "R$_{5}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:A simple tree with a hole-b} after adding \Vertex{6} and \Edge{5}}
\label{fig:Construction-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction}
\label{fig:Construction}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"'],
   {}
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 y [as={$\texttt{y}_{6}$}]
};
\end{tikzpicture}
\caption{\autoref{fig:Construction-b} after deleting \Edge{5}}
\label{fig:Change-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}[framed]
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"'],
   "$\texttt{z}_{8}$" [> "R$_{7}$"]
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 "$\texttt{y}_{6}$"
};
\end{tikzpicture}
\caption{\autoref{fig:Change-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Change-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Change}
\label{fig:Change}
\end{figure}

@@

\begin{figure}
% TODO: naive add that creates a conflict
% \begin{tikzpicture}
% \path (0,0)       node {\includegraphics[scale=0.4]{graphviz/wrapping/1.dot}};
% \path (0cm,-4cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/2.dot}};
% \path (0cm,-8cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/3.dot}};
% \path (0cm,-12cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/4.dot}};
% \path (0cm,-16cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/5.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (-0.5,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{3}$"'],
  "$\texttt{z}_{6}$" [> "R$_{5}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Change-b} after deleting \Edge{1}}
\label{fig:Wrapping-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"]
 }
};
\path (-0.5cm,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{5}$"'],
  "$\texttt{z}_{6}$" [> "R$_{5}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Wrapping-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{9}$"'] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{z}_{6}$" [> "R$_{5}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-b} after adding \Edge{9}}
\label{fig:Wrapping-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure}

@@

\begin{figure}
% \centering
% \begin{tikzpicture}
% \path (0,0)    node {\includegraphics[scale=0.75]{graphviz/move/1.dot}};
% \path (0,-5cm) node {\includegraphics[scale=0.75]{graphviz/move/2.dot}};
% \path (0,-9cm) node {\includegraphics[scale=0.75]{graphviz/move/3.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"]
 }
};
\path (0cm,-3cm) graph [graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{3}$"'],
  "$\texttt{z}_{6}$" [> "R$_{5}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-c} after deleting \Edge{9}}
\label{fig:Move-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.45\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{z}_{6}$" [> "R$_{5}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-a} after adding \Edge{11}}
\label{fig:Move-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \Vertex{2} from the left child to the right child of \Vertex{8}}
\label{fig:Move}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{z}_{6}$" [> "R$_{5}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{v}_{14}$" [> "R$_{15}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{v}_{14}$" [> "R$_{15}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{11}$"] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Different Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{v}_{14}$" [> "R$_{15}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Different Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{20}$" [> "R$_{21}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   },
   "$\texttt{y}_{22}$" [> "R$_{23}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{u}_{12}$" [> "L$_{13}$"'],
    "$\texttt{w}_{16}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{20}$" [> "R$_{21}$"],
    "$\texttt{y}_{22}$" [> "R$_{23}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{24}$" [> "L$_{23}$"'] -> {
    "$\texttt{x}_{26}$" [> "L$_{25}$"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
